---
title: "Assignment 7"
author: "Katrina Olsen"
format: html
editor: visual
---

# Moses Illusions

Moses illusions are cases where a speaker answers a question using common knowledge, even though the question itself is nonsensical and merely similar to a common question.

## Moses Illusion Example

**Common Knowledge Question:** "How many of each animal did *Noah* take on the arc?"\
**Correct Answer:** 2

**Moses Illusion Question:** "How many of each animal did *Moses* take on the arc?"\
**Moses Illusion Answer:** 2\
**Correct Answer:** "can't answer" / "NA" / etc.

## Data

Answers to Moses Illusion Questions and normal, control questions were collected.

### Answer Labels

-   Correct
-   Incorrect
-   Don't Know

### Examples

Examples for various answers and their labels, given the question type, are as follows:

| Question Type  | Question                                          | Answer       | Answer Label |
|----------------|---------------------------------------------------|--------------|--------------|
| No Illusion    | How many of each animal did Noah take on the arc? | 2            | Correct      |
| No Illusion    | How many of each animal did Noah take on the arc? | 1            | Incorrect    |
| Moses Illusion | How many of each animal did Noah take on the arc? | can't answer | Correct      |
| Moses Illusion | How many of each animal did Noah take on the arc? | 2            | Incorrect    |

: Table of Examples {#tbl-example}

And then any answers like "don't know" or "idk" get labeled as "Don't Know", no matter the question type.

# Data and Visualization

## Loading Data

Below you can see the packages and data we use for analysis.

```{r Loading packages and data}
#| warning: false

library(ggplot2)
library(tidyverse)

moses <- read_csv("moses_clean.csv")
questions <- read_csv('questions.csv')

```

```{r Loading data}
#| echo: false

moses.processed <-
  moses |> 
  inner_join(questions, by=c("ITEM", "CONDITION", "LIST")) |>
  select(ID, ITEM, CONDITION, QUESTION, ANSWER, CORRECT_ANSWER) |>
  mutate(ACCURATE = ifelse(CORRECT_ANSWER == ANSWER,
                           yes = "Correct",
                           no = ifelse(ANSWER == "dont_know",
                                       yes = "Don't Know",
                                       no = "Incorrect")),
         CONDITION = case_when(CONDITION == '1' ~ 'Illusion',
                               CONDITION == '2' ~ 'No Illusion',
                               CONDITION == '100' ~ 'Good Filler',
                               CONDITION == '101' ~ 'Bad Filler'))  
```

After some data manipulation, each question's answer is given an label from the [Answer Labels] described above. The method for labeling answer types based off the question type is performed as shown in @tbl-example.

## Data Visualization

```{r}
#| echo: false
#| warning: false
#| label: fig-bar

moses.processed |>
  filter(CONDITION %in% c('Illusion', 'No Illusion')) |>
  group_by(CONDITION, ACCURATE) |>
  summarise(Count = n()) |>
  ggplot() +
  aes(x = ACCURATE, y = Count, fill = CONDITION) +
  geom_bar(stat='identity', position = "dodge") +
  scale_fill_hue(direction = 1) +
  labs(
    x = "Type of Answers",
    y = "Counts",
    title = "Moses Illusion Effect on Answer Type Counts",
    fill = "Question Type",
  ) +
  theme_minimal()
```

```{r}
#| echo: false
#| warning: false
#| label: fig-line

moses.processed |>
  filter(CONDITION %in% c('Illusion')) |>
  group_by(ITEM, ACCURATE) |>
  summarise(Count = n()) |>
  ggplot() +
  aes(x = ITEM, y = Count, color=ACCURATE) +
  geom_line() +
  scale_fill_hue(direction = 1) +
  labs(
    x = "Question Number",
    y = "Percentage",
    title = "Answer Type Percentages per Moses Illusion Question",
    color = "Answer Type",
  ) +
  theme_minimal()

```

```{r}
#| echo: false
#| warning: false
#| label: fig-dots


moses.processed |>
  mutate(NUM_ANSWER = as.numeric(ANSWER)) |>
  mutate(ITEM_Label = as.character(ITEM)) |>
  na.omit() |>
  ggplot() +
  aes(x = ITEM_Label, y = NUM_ANSWER, colour = ACCURATE) +
  geom_point(shape = "circle", size = 1.5) +
  scale_fill_hue(direction = 1) +
  labs(
    x = "Question IDs",
    y = "Submitted Numeric Answers",
    title = "Numeric Answers Submitted per Question ID",
    color = "Answer Types",
  ) +
  scale_color_manual(values=c('black','grey'))+
  theme_minimal()

```

------------------------------------------------------------------------

## Findings

As you can see, @fig-bar is particularly insightful for how the presence of an illusion in a question affects the count of incorrect answers.

### Meta information

```{r}
sessionInfo()
```
